Converging High-Throughput and High-Performance Computing: A Case Study

### 2017-03-27 nge.tex
quick read, minor tweaks and a comment in 6.1 and 6.2
  did not touch 6.3

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.} As seen in
\S\ref{sec:panda_deployment}, the absence of wide area network connectivity on
Titan's worker nodes was one of the main reasons for PanDA Broker not to
implement pilots. As discussed in \S\ref{sec:panda_titan}, the absence of pilots
imposes the static coupling between MPI scripts submitted to the PBS batch
system and detector simulations, and development tailored to each type of
payload that needs to be executed.

@@

The support of workload generations would enable a more efficient use of the
backfill availability of walltime. Currently, when a set of simulations ends
also the PBS job ends, independently on whether more walltime would still be
available. With a pilot, more simulations could be executed so to utilize all
the available walltime, while avoiding further job packaging and submission
overheads.

>>>>

\subsection{Rationale} \aanote{I think that the names of the states should be
removed. They are meaningless without the figures. I left them just in case we
decide to reintroduce the figures.}\mtnote{Done.} As seen in
\S\ref{sec:panda_deployment}, the absence of wide area network
\jhanote{admittedly i haven't read earlier section in question  carefully, but
i'm a bit confused about the use of "wide area". wide area is typically used
for cross data center} connectivity on Titan's worker nodes was one of the
main reasons for PanDA Broker not to implement pilots. As discussed in
\S\ref{sec:panda_titan}, the absence of pilots imposes the static coupling
between MPI scripts submitted to the PBS batch system and detector
simulations, and development tailored to each type of payload that needs to be
executed.

@@

The support of  multiple workload generations would enable a more efficient
use of the backfill availability of walltime. Currently, when a set of
simulations ends, the PBS job also ends, independent of whether more wall-time
would still be available. With a pilot, more simulations could be executed so
to utilize all the available wall-time, while avoiding further job packaging
and submission overheads.
